Parsing Postfix log files

### 2008-07-07 doc/logparser.tex
Copied some of the things I learned writing the SGAI paper. I haven't decided either way on using Times New Roman or not. Reordered some stuff to group similar things together. Switched to varioref for references. Extract some more warnings after running make.

% Useful stuff for math mode.
\usepackage{amstext}
% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\PLP{}}
\newcommand{\parsernames}{\PLP{}'s}
% Include images
\usepackage[final]{graphicx}
% Change how nested enumerate environments are labelled.
\renewcommand{\labelenumii}{\roman{enumii}:}
\renewcommand{\refname}{Bibliography}
% Add the bibliography into the table of contents.
\usepackage[section,numbib]{tocbibind}
% Provides commands to distinguish between pdf and dvi output.
\usepackage{ifpdf}

% global=true prevents acronyms being expanded twice
\usepackage[global=true,acronym=true,style=altlist,number=none,toc=true]{glossary}
\makeglossary{}
\makeacronym{}

% When creating a \PDF{} make the table of contents into links to the pages
% (without horrible red borders) and include bookmarks.  The title and
% author don't work - I think either gnuplot or graphviz clobbers it.
% hyperfootnotes need to be disabled to avoid breaking footmisc, but they
% still seem to work, somehow.
\ifpdf{}
    \usepackage[pdftex,hyperfootnotes=false]{hyperref}
\else{}
    \usepackage[dvips,hyperfootnotes=false]{hyperref}
\fi{}
\hypersetup{
    pdftitle    = {Parsing Postfix log files},
    pdfauthor   = {John Tobin},
    final       = true,
    pdfborder   = {0 0 0},
%    breaklinks  = true,
}
% This is necessary for URLs in the bibliography; I dunno why the url
% package doesn't work; don't include it when generating \PDF{} output.
\ifpdf{}
\else{}
    \usepackage{breakurl}
\fi{}
\usepackage{lastpage}

% Extra footnote functionality, including references to earlier footnotes.
\usepackage{footmisc}

% Sort numbers where there are multiple citations.  Doesn't appear to have
% any effect, though it does reduce the space between numbers.
\usepackage{cite}

@@

% Replacement for \ref{}, adds the page number too.
\newcommand{\refwithpage}[1]{%
    \empty{}\ref{#1} [p.~\pageref{#1}]%
}
% section references, automatically add \textsection
\newcommand{\sectionref}[1]{%
    \textsection{}\refwithpage{#1}%
}

@@

\newcommand{\numberOFlogFILES}[0]{%
    93%
}

@@

% This may keep hyperref happy about the Abstract entry in the table of
% contents.
\newcounter{dummy}

@@

XXX POSSIBLE CONFERENCES\@: AICS'S AI-2008 IN CORK, AND SGAI IN CAMBRIDGE
IN DECEMBER\@.

@@

XXX IS THERE A SYMBOL FOR APPENDIX, LIKE \textsection{} FOR SECTIONS\@?

@@

>>>>

% Useful stuff for math mode.
\usepackage{amstext}
% Include images
\usepackage[final]{graphicx}
% Add the bibliography into the table of contents.
\usepackage[section,numbib]{tocbibind}
% Create a label for the last page.  Might be useful for "page 23/79" or
% something.
\usepackage{lastpage}

% Extra packages recommended by Springer: they change the fonts from
% Computer Modern to something else and tells Latex to use scalable fonts.
\usepackage{type1cm}
%\usepackage{mathptmx}
%\usepackage{helvet}
%\usepackage{courier}
% Extra footnote functionality, including references to earlier footnotes.
\usepackage{footmisc}

% Sort numbers where there are multiple citations.  Doesn't appear to have
% any effect (probably clashes with varioref or hyperref), though it does
% reduce the space between numbers.
\usepackage{cite}

% Acronyms and glossary entries.
% global=true prevents acronyms being expanded twice
\usepackage[global=true,acronym=true,style=altlist,number=none,toc=true]{glossary}
\makeglossary{}
\makeacronym{}

% Produce nicer references, e.g. "section 4.3 on the next page"
% Must be loaded before hyperref.
\usepackage{varioref}
% Warnings rather than errors when references cross page boundaries.
\vrefwarning{}
% Errors when loops are encountered
\vrefshowerrors{}
% Shorten the text used for references with page numbers.
\renewcommand{\reftextfaraway}[1]{%
    [p.~\pageref{#1}]%
}
% Replacement for \ref{}, adds the page number too.
\newcommand{\refwithpage}[1]{%
    \empty{}\vref{#1}%
    %\empty{}\ref{#1} [p.~\pageref{#1}]%
}
% section references, automatically add \textsection
\newcommand{\sectionref}[1]{%
    \textsection{}\vref*{#1}%
    %\textsection{}\refwithpage{#1}%
}

% Provides commands to distinguish between pdf and dvi output.
\usepackage{ifpdf}
% When creating a \PDF{} make the table of contents into links to the pages
% (without horrible red borders) and include bookmarks.  The title and
% author don't work - I think either gnuplot or graphviz clobbers it.
% hyperfootnotes need to be disabled to avoid breaking footmisc, but they
% still seem to work, somehow.
\ifpdf{}
    \usepackage[pdftex,hyperfootnotes=false]{hyperref}
\else{}
    \usepackage[dvips,hyperfootnotes=false]{hyperref}
    % This is necessary for wrapping URLs in the bibliography when
    % producing a dvi, but causes problems when generating \PDF{} output.
    \usepackage{breakurl}
\fi{}
\hypersetup{
    pdftitle    = {Parsing Postfix log files},
    pdfauthor   = {John Tobin},
    final       = true,
    pdfborder   = {0 0 0},
}

\renewcommand{\refname}{Bibliography}
% New formatting commands.

@@

@@

% Constant values.
\newcommand{\numberOFlogFILES}[0]{%
    93%
}

@@

% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\PLP{}}
\newcommand{\parsernames}{\PLP{}'s}

% This keeps hyperref fairly happy about the Abstract entry in the table of
% contents.
\newcounter{dummy}

@@

@@

@@

XXX EXPLAIN THE X-AXIS --- MADS THOUGHT IT WAS UNCLEAR\@.
